Report with embedded R code

### 2022-04-04 Project/FinalReport.Rmd
Update FinalReport.Rmd

### Description of the variables: 
\n 
**d.snowpack.10.11** = days with snowpack winter 2010-2011 
**wTmin.10.11** = minimum temperature winter (C) at plant height 2010-2011 
**Dec.FebTav.10.11** = mean temperature at plant height from Dec1st 2010 - Feb 28th 2011 
**d.grows.11** = \# days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost) **GDD.grows.11** = \# growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011 
**GDD.yr.11** = \# growing degree days in 2011 (ie not truncated to estimated growing season) 
**avmaxminTJuly.11** = mean July 2011 temperature (C) calculated from daily min and max T: 
mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax) 
**avTJuly.11** = mean July 2011 temperature (C) calculated from raw data (ie \>2 measurements per day)

@@

### Description of the variables: 
\n 
**year** = year plants were active 
**transect** = elevational transect (where NK = Nakiska and HB = Hailstone Butte) 
**site** = site seeds were transplanted into. L = low elevation, M = mid-elevation (range centre), H = high-elevation (\~100 m below range edge), E or HE = high-elevation range edge, A = above range (HB), A1 = 1st site above the range at NK, A2 = second site above the range at NK 
**treat** = treatment in warming experiment. TR = normal transplant (control), OTC = Open topped warming chambers (warmed), dormant = plants found \> 1 year after seeds planted 
**Source** = source population: low-elevation from that transet (L), mid-elevation from that transect (M), high-elevation (within 100 masl of absolute high-elevation range edge) from that transect (H), edge (absolute high-elevation range edge E), high-elevation (2000 m) populations on neighbouring Moose Mountain (MT) and Fortress Mountain (F), and seeds produced by plants transplanted above the range the previous year (A) 
**plant** = plantID within each 5x5 subplot (row.column from 1.1 = topleft plant to 5.5 = bottom right plant) 
**tbo** = top bitten off by mammal. 0 = no, plant intact, 1 = top bitten off the primary stem, 2 = top bitten off some secondary stalks but primary stem intact 
**Ln.tot** = total leaf nodes (each leaf node produces 2 leaves), including primary, secondary and tertiary stems 
**Fr.tot** = total fruits from all stems
**aveseed1** = average number of seeds per fruit from primary stem fruits 
**aveseed2** = average number of seeds per fruit from secondary stem fruits 
**totgoodseed** = total viable seed produced by the plant 
**totbadseed** = total non-viable seed produced by the plant

@@

\n

@@

### Table 1
![pca analysis table 1](https://github.com/zazauwu/432_Group5/blob/main/Project/Figure/pca%20table.png)
## Ploting PCA

>>>>

### Description of the variables:

**d.snowpack.10.11** = days with snowpack winter 2010-2011

**wTmin.10.11** = minimum temperature winter (C) at plant height 2010-2011

**Dec.FebTav.10.11** = mean temperature at plant height from Dec1st 2010 - Feb 28th 2011

**d.grows.11** = \# days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost)

**GDD.grows.11** = \# growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011

**GDD.yr.11** = \# growing degree days in 2011 (ie not truncated to estimated growing season)

**avmaxminTJuly.11** = mean July 2011 temperature (C) calculated from daily min and max T: 
mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax)

**avTJuly.11** = mean July 2011 temperature (C) calculated from raw data (ie \>2 measurements per day)

@@

### Description of the variables:

**year** = year plants were active

**transect** = elevational transect (where NK = Nakiska and HB = Hailstone Butte)

**site** = site seeds were transplanted into. L = low elevation, M = mid-elevation (range centre), H = high-elevation (\~100 m below range edge), E or HE = high-elevation range edge, A = above range (HB), A1 = 1st site above the range at NK, A2 = second site above the range at NK

**treat** = treatment in warming experiment. TR = normal transplant (control), OTC = Open topped warming chambers (warmed), dormant = plants found \> 1 year after seeds planted

**Source** = source population: low-elevation from that transet (L), mid-elevation from that transect (M), high-elevation (within 100 masl of absolute high-elevation range edge) from that transect (H), edge (absolute high-elevation range edge E), high-elevation (2000 m) populations on neighbouring Moose Mountain (MT) and Fortress Mountain (F), and seeds produced by plants transplanted above the range the previous year (A)

**plant** = plantID within each 5x5 subplot (row.column from 1.1 = topleft plant to 5.5 = bottom right plant)

**tbo** = top bitten off by mammal. 0 = no, plant intact, 1 = top bitten off the primary stem, 2 = top bitten off some secondary stalks but primary stem intact

**Ln.tot** = total leaf nodes (each leaf node produces 2 leaves), including primary, secondary and tertiary stems

**Fr.tot** = total fruits from all stems

**aveseed1** = average number of seeds per fruit from primary stem fruits

**aveseed2** = average number of seeds per fruit from secondary stem fruits

**totgoodseed** = total viable seed produced by the plant

**totbadseed** = total non-viable seed produced by the plant

@@

@@

### Table 1
```{r, echo=FALSE, out.width="50%", fig.align = 'center'}
knitr::include_graphics("./Figure/pca_table.png")
```
Given by the table, in the principal component analysis, the most prominent biological factor (eigenvalue: 1.897, total variance explained: 63.2%) was total leaf nodes, including primary, secondary and tertiary stems.

## Ploting PCA
